SPANG: A SPARQL Client with One-Liners, Template Libraries, and API

### 2020-09-21 paper.tex
fix typo
change title and modify sections

\title{SPANG: a SPARQL client with templating, one-liner functionalities, and API}
\titlerunning{SPANG: a SPARQL client with templating, one-liner, and API}
\author{Hirokazu Chiba\orcidID{0000-0003-4062-8903}}
\authorrunning{H. Chiba}
\institute{Database Center for Life Science, Chiba 277-0871, Japan\\
\email{chiba@dbcls.rois.ac.jp}
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
%The abstract should briefly summarize the contents of the paper in 15--250 words.
%How can we maximize the value of accumulated SPARQL queries? 
SPARQL is a key component of the Semantic Web, thus the reusability of SPARQL is crucial for maximizing the productivity on the Semantic Web.
Whereas an increasing number of datasets have been published in the Resource Description Framework (RDF) and the SPARQL standard allows interoperable framework for querying the RDF datasets, reuse of SPARQL queries remains limited. We present SPANG, a framework to make SPARQL queries more reusable using templating engine, one-liner functionality, and API. Here we demonstrate its use cases for making SPARQL queries more reusable; assigning a set of metadata for annotating a SPARQL query, which enables to identify SPARQL query and provides useful information for the query; parameterizing SPARQL queries, which makes each query reusable in different settings; assigning globally unique and stable identifier for each query; and constructing a server to provide indices of SPARQL queries. SPANG makes SPARQL queries more reusable in the local system or across the Web, and leads to the construction of eco-system where SPARQL queries are shared to maximize the productivity of the Semantic Web developers and users. SPANG is available at \url{https://spang.dbcls.jp/}.

@@

SPANG was originally developed as a command-line SPARQL client~\cite{spang}, and now it is re-implemented in JavaScript using Node.js. Thus, it can be called not only in command line but also in the JavaScript code used to construct a website.

We also developed a SPANG sever, where SPARQL queries can be executed on the browser or through REST API (\url{https://spang.dbcls.jp/}).
SPANG server is developed using Ruby on Rails, and it can run on Docker.
Thus, users can also run a SPANG server on their own.

@@

@@

>>>>

\title{SPANG: A SPARQL Client with One-Liners, Template Libraries, and API}
\titlerunning{SPANG: A SPARQL Client with One-Liners, Template Libraries, and API}
\author{Hirokazu Chiba\orcidID{0000-0003-4062-8903}}
\authorrunning{H. Chiba}
\institute{Database Center for Life Science, Chiba 277-0871, Japan\\
\email{chiba@dbcls.rois.ac.jp}
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
%The abstract should briefly summarize the contents of the paper in 15--250 words.
%How can we maximize the value of accumulated SPARQL queries? 
SPARQL is a key component of the Semantic Web, thus the reusability of SPARQL is crucial for maximizing the productivity on the Semantic Web.
Whereas an increasing number of datasets have been published in the Resource Description Framework (RDF) and the SPARQL standard allows interoperable framework for querying the RDF datasets, reuse of SPARQL queries remains limited. We present SPANG, a framework to make SPARQL queries more reusable using templating engine, one-liner functionality, and API. Here we demonstrate its use cases for making SPARQL queries more reusable; assigning a set of metadata for annotating a SPARQL query, which enables to identify SPARQL query and provides useful information for the query; parameterizing SPARQL queries, which makes each query reusable in different settings; assigning globally unique and stable identifier for each query; and constructing a server to provide indices of SPARQL queries. SPANG makes SPARQL queries more reusable in the local system or across the Web, and leads to the construction of eco-system where SPARQL queries are shared to maximize the productivity of the Semantic Web developers and users. SPANG is available at \url{https://spang.dbcls.jp/}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%
\section{SPANG Overview}
%%%%%%%%%%%%%%%%%%%%%%%%

The SPANG~\cite{spang} project started aiming at maximizing the usability of SPARQL queries. 
SPANG was originally developed as a command-line SPARQL client~\cite{spang}, and now it is re-implemented in JavaScript using Node.js. Thus, it can be called not only in command line but also in the JavaScript code used to construct a website.

@@

We also developed a SPANG server, where SPARQL queries can be executed on the browser or through REST API (\url{https://spang.dbcls.jp/}).
SPANG server is developed using Ruby on Rails, and it can run on Docker.
Thus, users can also run a SPANG server on their own.

%%%%%%%%%%%%%%%%%%%%%%
\section{Related Work}
%%%%%%%%%%%%%%%%%%%%%%

SPARQL tempalting mechanisms have been implemented in various projects. Based on the templating mechanisms, SPARQL libraries have been implemented, such as Bioqueries~\cite{bioqueries}. Bioqueries have tried to collect SPARQL queries as community effort. It increase the findability and reusability.
However, the query can only be executed on the web site.
Users should copy and paste the queries into their own software.
In contrast, we tried to build a software network on top of the Semantic Web platform.

@@

\bibitem{bioqueries}
García-Godoy, M. J., Navas-Delgado, I., & Aldana-Montes, J. (2011, December). Bioqueries: a social community sharing experiences while querying biological linked data. In Proceedings of the 4th international workshop on semantic web applications and tools for the life sciences (pp. 24-31).
